\section{Evaluation Plan}
\label{sec:evaluation}

The three thrusts will be evaluated through a combination of
controlled testbed experiments, collaborations with industry and
critical-infrastructure partners, and end-to-end case studies.

\paragraph{Reference testbeds.}
We will build a small number of reference open-source stack testbeds
in our lab, spanning sectors with distinct threat models: a
healthcare-records stack (an EHR-style deployment built around
PostgreSQL, Keycloak for identity, a FHIR-compatible application
tier, Kafka for integration events, and a Kubernetes control plane);
a financial-services transaction-processing stack (a payments-style
deployment with a CockroachDB/PostgreSQL data tier, a gRPC-based
microservice mesh under Istio, Redis for session and rate-limiting
state, and an OPA-based policy layer); and a public-service portal
stack (a citizen-facing deployment combining nginx and HAProxy as
edge tiers, a Django or Rails application tier, Elasticsearch for
search, and MinIO for document storage). These testbeds are small
enough to allow ground truth about their configuration and
vulnerabilities to be established by hand, but representative enough
that findings generalize. For each testbed we will maintain a
versioned KB and a seeded set of known vulnerabilities (drawn from
historical CVEs applicable to the specific component versions and
from deliberately-introduced misconfigurations) against which
\sysname's precision and recall can be measured.

\paragraph{Partner environments.}
We will work with industry partners and critical-infrastructure
operators to evaluate \sysname against real operational environments.
The evaluation will focus on the KB and Observer Agents (which are
the components deployable against production systems) and on the
ability of our framework to replicate partner environments from the
evidence partners already have. We expect partners to provide
documentation and logs, and---under appropriate safeguards---read-only
observation opportunities. The Red Team Agents will be run only
against the resulting twin.

\paragraph{UCSB campus as a secondary target.}
As an intermediate-scale, non-dedicated environment, we will also
develop Observer Agents for UCSB internal networks and service
deployments (which themselves are built from many of the same
open-source components our reference testbeds use). This gives us a
large, heterogeneous, cooperative target on which we can refine
observation techniques before applying them to more sensitive
partner environments.

\paragraph{Metrics.}
We will report the following metrics across thrusts:
\emph{KB coverage and freshness} (fraction of ground-truth entities
represented, median staleness of their properties);
\emph{observation risk} (measured operational impact on targets, with
zero incidents as a hard requirement);
\emph{twin fidelity} (attack reproducibility and behavioral divergence,
as defined in \S\ref{sec:thrust2});
\emph{analysis yield} (number of confirmed vulnerabilities per
twin-hour of analysis); and
\emph{human efficiency} (findings validated per analyst-hour, and
true-positive rate of escalated findings).

\paragraph{Baselines and comparisons.}
Where possible, we will compare \sysname's findings against the
results of traditional manual penetration tests performed on the same
testbeds. We will also compare against purely component-level
analyses (fuzzing alone, static analysis alone), to measure the
marginal contribution of multi-step planning. Finally, we will
conduct ablation studies to quantify the contribution of each agent
role and of the LLM/classical-planner hybrid.
