\section{Research Thrusts}
\label{sec:thrusts}

The proposed work is organized into three research thrusts that
correspond to the major technical challenges underlying \sysname:
\emph{capturing} a cyberphysical system's configuration and behavior
(Thrust~1, \S\ref{sec:thrust1}), \emph{replicating} it as a
controlled-fidelity digital twin (Thrust~2, \S\ref{sec:thrust2}), and
\emph{analyzing} that twin through agentic red teaming
(Thrust~3, \S\ref{sec:thrust3}). Although the thrusts are presented in
this order---and the timeline in \S\ref{sec:timeline} phases them
accordingly---they are deeply coupled: fidelity requirements from
Thrust~3 drive replication decisions in Thrust~2, which in turn drive
observation priorities in Thrust~1. Each thrust is accompanied by
specific research questions, the techniques we propose to investigate,
and success criteria.

%% =============================================================
\subsection{Thrust 1: Capturing CPS Configurations}
\label{sec:thrust1}

\subsubsection*{Research questions}
\textbf{(RQ1.1)} What is the right representation for a living,
partially-known model of a cyberphysical system, such that AI agents
can reason about it, update it incrementally, and flag contradictions?
\textbf{(RQ1.2)} What observation techniques yield the highest
information per unit of operational risk when applied to a production
\cps?
\textbf{(RQ1.3)} How should static documentation and dynamic
observations be fused when they disagree, and when should the system
escalate to a human rather than resolving the disagreement itself?

\subsubsection{A Hybrid Knowledge Base}

A recurring observation in our preliminary work is that neither a
purely-structured representation nor a purely-unstructured one is
sufficient to capture a \cps.  A graph database cleanly expresses
``PLC-A is connected to HMI-B over subnet S via switch X'' but
awkwardly expresses ``the vendor documentation notes, in §4.2, that
firmware revisions below 2.3.1 mishandle malformed read-multiple-registers
requests.''  A vector database cleanly expresses the latter but
poorly supports topological queries.  We therefore propose a
\emph{hybrid} knowledge base with two coordinated stores:

\begin{itemize}[leftmargin=1.3em,itemsep=0.1em,topsep=0.2em]
  \item A property-graph database (prototyped in Neo4j) storing
  \emph{entities} (hosts, services, devices, users, data stores,
  network segments, policies), \emph{relationships} (connects-to,
  depends-on, authenticates-via, trusts, monitors), and
  \emph{properties} (versions, CPEs, ownership, confidence, provenance).
  The schema is closed and curated; new node and edge types are
  introduced through a controlled process rather than by agents on
  their own authority.
  \item A vector database (prototyped in Qdrant or Weaviate) storing
  natural-language content---manual sections, configuration snippets,
  policy text, log samples, ticket narratives---each with a pointer
  back to the graph entity or relationship it describes, and a
  timestamp and source URI for provenance.
\end{itemize}

The two stores are linked by \emph{anchor edges}: every vector entry
has one or more anchor edges into the graph, and every graph entity
can enumerate the vector entries that reference it. Agent queries
typically traverse both: ``given this PLC's vendor and firmware
version, what does the documentation say about authentication defaults,
and does the network topology around this PLC contradict those
defaults?'' We will investigate whether a structured prompting
convention---retrieval over the vector store constrained by a
graph-traversal filter---yields better agent reasoning than either
store alone.

\paragraph{Research sub-problem: confidence and contradiction.}
Unlike a configuration-management database, which assumes its contents
are true, the \sysname KB must represent uncertainty and disagreement.
We propose to extend each fact with a \emph{confidence score}
(initially derived from source type: vendor documentation is trusted
less than observed network behavior, which is trusted less than
cryptographic attestation), an \emph{agreement set} (the observations
that support the fact), and a \emph{disagreement set} (the observations
that contradict it). An open research question is how to calibrate
these scores in a way that downstream agents---particularly Red Team
Agents, whose attack plans may hinge on a single load-bearing fact---
can use.

\subsubsection{Observation Techniques}

Observer Agents gather information about the running \cps through
\emph{strictly passive} means. We propose to investigate five
complementary techniques, each with distinct coverage, cost, and
deployability profiles.

\paragraph{Passive network analysis.}
Observer Agents consume packet captures from network taps or SPAN
ports, using protocol dissectors to reconstruct flows and sessions.
For industrial protocols, we will extend existing open-source
dissectors (e.g., for Modbus, DNP3, OPC~UA) and build LLM-assisted
dissectors for proprietary variants, using the vendor documentation
stored in the KB as few-shot context. A key research question is
\emph{flow attribution}: given a flow between two hosts, can the
Observer infer the application-layer purpose (e.g., ``historian
polling an RTU every 3~s'') rather than just the protocol?

\paragraph{Log monitoring.}
Cyberphysical environments produce logs in radically inconsistent
formats: structured JSON from modern services, line-oriented
syslog-like records from legacy Unix daemons, proprietary binary
formats from industrial controllers, and free-form text from vendor
appliances. We propose an LLM-based log normalization pipeline that
maps arbitrary log records into a shared ontology (event type,
source, target, outcome, attributes) rooted in the KB's graph schema.
The research contribution here is not the use of LLMs for
log parsing---that is now standard---but the closed-loop use of the KB
as grounding: because the agent knows what hosts and services exist,
it can validate parses against plausible entities and flag spurious
matches.

\paragraph{API monitoring.}
Modern \cps deployments increasingly use microservice-style
architectures at the supervisory layer. Where this is the case, we
will use service-mesh facilities (e.g., Istio with Envoy) or eBPF-based
probes to capture inter-service API calls without touching application
code. This gives the Observer access to semantics---which service
called which API on which resource---that network-layer observation
cannot.

\paragraph{Configuration monitoring.}
Many \CPSs are increasingly managed through configuration managers
such as Ansible, Puppet, Chef, or SaltStack. Where such a manager is
present, an Observer Agent with read-only access to its inventory and
playbooks can extract a large fraction of the system's intended
configuration directly, without ever touching a production host. We
will build adapters for the major open-source configuration managers
and, where industrial vendors provide proprietary management APIs,
evaluate the cost of extending the approach.

\paragraph{Security-tool integration.}
Finally, Observer Agents will integrate with existing security tooling
when it is present: endpoint detection and response (EDR) agents,
industrial IDS products (e.g., those in the Nozomi/Claroty/Dragos
category), and security information and event management (SIEM)
systems. The value here is not to replace these tools but to treat
their alerts as observations---signals that the KB should record and
that Red Team Agents should consider when modeling what an attacker
would see.

\paragraph{Research sub-problem: observation planning as an optimization
problem.}
Observer Agents do not enjoy unlimited visibility. SPAN ports are
scarce; storage and bandwidth are finite; some network segments can
only be observed through a single, contended vantage point. We propose
to formulate observation planning as a constrained optimization: given
a set of KB entities of interest, a set of possible vantage points,
and a budget, maximize the expected information gain about the
uncertain parts of the KB. We will investigate whether this problem
admits a tractable approximation and whether solutions computed by a
classical optimizer can be improved by LLM-guided reasoning about
which facts are security-relevant.

\subsubsection{Expected Outcomes of Thrust~1}
\begin{itemize}[leftmargin=1.3em,itemsep=0.1em,topsep=0.2em]
  \item A schema and open-source implementation of a hybrid,
  uncertainty-aware knowledge base for cyberphysical systems.
  \item An extensible library of passive observation modules, including
  adapters for industrial protocols, log normalizers, service-mesh
  probes, configuration-manager readers, and SIEM connectors.
  \item An evaluation, on reference \CPSs (see
  \S\ref{sec:evaluation}), of the coverage, latency, and
  operational-risk profile of the above techniques.
\end{itemize}

%% =============================================================
\subsection{Thrust 2: Replicating CPSs}
\label{sec:thrust2}

\subsubsection*{Research questions}
\textbf{(RQ2.1)} What does it mean for a digital twin to be
``sufficiently faithful'' for security analysis, and how can that
property be measured?
\textbf{(RQ2.2)} Given that a perfectly faithful twin of a large \cps
is infeasible, how should a replication algorithm trade fidelity
against cost, and what parameters should the operator be able to
control?
\textbf{(RQ2.3)} For components that cannot be emulated directly, how
can an observed behavior be turned into a mock that is sound for
security analysis?

\subsubsection{Controlled-Fidelity Replication}

The naive approach to digital twin construction---replicate every
component---fails for three reasons: large \CPSs contain hundreds or
thousands of similar devices, many of which are variants of the same
underlying platform; the firmware and tooling needed to run some
components in emulation is simply not available; and the operational
cost of running a full-scale replica often exceeds the cost of the
original. \sysname's replication approach is therefore explicitly
\emph{representational} rather than \emph{exhaustive}: the twin
preserves the features that matter for security analysis and
deliberately abstracts away features that do not.

We formalize this as a \emph{controlled-fidelity replication problem}.
Given the KB's inventory of components, the twin is characterized by
three parameters:

\begin{description}[leftmargin=1.6em,style=nextline,itemsep=0.15em,topsep=0.3em]
  \item[Diversity ($D$).] Every equivalence class of components in
  the original system (defined by vendor, model, firmware version, and
  role) must be represented by at least one instance in the twin.
  This is the minimum condition for the Red Team to encounter every
  vendor-specific bug class present in the real system.
  \item[Topology representation ($T$).] Many vulnerabilities depend
  on \emph{patterns} of connectivity rather than individual links
  (e.g., ``controller and engineering workstation share a flat
  segment'', ``historian is reachable from the corporate network via
  a single firewall rule''). Our algorithm enumerates recurring
  topological patterns in the original system and guarantees that
  each pattern appears at least once in the twin.
  \item[Data representation ($R$).] Some attacks depend on the data
  being processed (e.g., injection attacks against a historian with
  particular field widths; process-logic attacks that depend on
  realistic setpoint ranges). The twin is populated with synthetic
  data whose statistical properties match the original, under a
  privacy constraint that excludes personally-identifiable and
  safety-sensitive records.
\end{description}

Given $(D, T, R)$, the replication algorithm solves a set-cover-like
problem: select a minimum-size set of component instances that
covers all equivalence classes, all required topological patterns,
and all required data-distribution targets. We will investigate
approximation algorithms for this problem and develop an
operator-facing interface that exposes $(D, T, R)$ as tunable knobs,
with default settings derived from the KB's risk model.

\paragraph{Research sub-problem: quantifying fidelity.}
A central open question is how to measure whether a twin is
``faithful enough.'' We propose two complementary metrics. The first
is \emph{attack reproducibility}: for a seeded set of known-real
vulnerabilities (injected deliberately into the real system and
documented in the KB, or drawn from historical CVE reports on identical
equipment), what fraction can the Red Team reproduce against the
twin? The second is \emph{behavioral divergence}: for a stream of
observations on the real system, how often does the twin produce a
statistically distinguishable response to the same stimulus? We will
investigate both metrics empirically on reference testbeds.

\subsubsection{Replicating Specialized Hardware}

A substantial fraction of the components in a typical \cps cannot be
reproduced by conventional virtualization. These include programmable
logic controllers running vendor-proprietary firmware on ARM or PowerPC,
field devices with custom ASICs, and appliances whose hardware
dependencies are not documented. Our group has spent the last decade
developing techniques to analyze exactly these kinds of systems, and
\sysname builds directly on that foundation.

\paragraph{Full-system emulation.}
Where the hardware platform is well-understood and the firmware can
be extracted, we use QEMU-based full-system emulation. Our earlier
work on \emph{Avatar} and its successors provides a starting point
for orchestrating emulation at this level.

\paragraph{Abstraction-layer re-hosting.}
For firmware that depends on specific peripherals or hardware timing
that QEMU cannot emulate, we will extend our HALucinator
approach [Clements et al., USENIX Security 2020], which intercepts firmware calls at the
hardware-abstraction-layer boundary and replaces them with
host-provided implementations. This has been shown to scale to
firmware images for which a full hardware model is unavailable, and
it is a natural fit for \sysname's twin construction because the
Replication Agent can generate HAL handlers automatically from
observed interface descriptions in the KB.

\paragraph{Behavioral mock synthesis.}
For components where even re-hosting is infeasible---typically
because the firmware cannot be extracted, or because the device is
effectively a black box---we will apply ideas from our
Conware [Spensky et al., AsiaCCS 2021] work, which automatically models hardware
peripherals from recorded interactions. A Replication Agent will
construct a finite-state model of the component's externally visible
behavior from Observer traces, and instantiate that model as a mock
service that responds to queries as the real component would. Mocks
are not a substitute for real execution, and we are careful to label
findings produced against them as such; but they allow the surrounding
system to be reasoned about without the mocked component becoming a
hole that disables all analysis.

\paragraph{Human escalation for irreducible gaps.}
Some components will resist all of the above approaches: the firmware
is encrypted and the key is unknown, the hardware includes an HSM
whose secrets cannot be extracted, the device is a purely physical
actuator with no digital interface. In these cases, the Replication
Agent surfaces a structured request to the human operator, who may
provide additional information, authorize an offline analysis of a
lab unit, or declare the component out of scope for the current twin.

\subsubsection{Expected Outcomes of Thrust~2}
\begin{itemize}[leftmargin=1.3em,itemsep=0.1em,topsep=0.2em]
  \item A formalization of the controlled-fidelity replication problem
  and one or more approximation algorithms.
  \item Metrics for quantifying twin fidelity, together with an
  empirical evaluation on reference \CPSs.
  \item Open-source tooling that extends QEMU, HALucinator, and
  Conware with agent-driven configuration and mock synthesis.
\end{itemize}

%% =============================================================
\subsection{Thrust 3: Analyzing CPSs}
\label{sec:thrust3}

\subsubsection*{Research questions}
\textbf{(RQ3.1)} How should component-level vulnerability analyses
(fuzzing, static analysis, symbolic execution) be scheduled and
composed against a digital twin of non-trivial size?
\textbf{(RQ3.2)} Can multi-step attack plans generated by AI-planning
techniques and refined by LLM-based reasoning discover vulnerabilities
that component-level analyses miss?
\textbf{(RQ3.3)} How should an agentic red team triage its own
findings before escalating to a human, so that the human's time is
spent on attacks that are both likely real and likely
high-consequence?

\subsubsection{Component-Level Analyses}

The twin is, by design, a controllable and repeatable target. This
allows a wide range of analyses that would be unsafe against the real
system:

\begin{itemize}[leftmargin=1.3em,itemsep=0.1em,topsep=0.2em]
  \item \emph{Coverage-guided fuzzing} of services and firmware, using
  tools such as AFL++\ and LibAFL against network-accessible and
  emulated components, including industrial protocol fuzzers seeded
  with corpora drawn from Observer traffic captures.
  \item \emph{Static analysis} of firmware images and application
  binaries using the \texttt{angr} binary-analysis framework
  (co-developed by the PIs) and LLM-assisted bug-pattern detectors
  that specialize in industrial protocol handling.
  \item \emph{Symbolic execution} for authentication and authorization
  logic, where the state space is small enough to explore exhaustively.
  \item \emph{Configuration analysis} that evaluates the twin's
  configuration against a library of known misconfiguration patterns
  (default credentials, permissive firewall rules, insecure
  cryptographic settings, and \cps-specific patterns such as
  ``engineering workstation reachable from OT-to-IT DMZ'').
\end{itemize}

Each component-level analysis produces \emph{atomic findings}: concrete
weaknesses characterized by a precondition (what an attacker must
already have in order to exploit the weakness) and a postcondition
(what the attacker gains). Atomic findings are pushed into the KB,
where they become available to the system-level planner.

\subsubsection{System-Level Multi-Step Attack Planning}

The central intellectual claim of Thrust~3 is that individual atomic
findings, while useful, are not where the most severe \cps
vulnerabilities live. Real incidents---Stuxnet, the Ukraine grid
attacks, the Colonial Pipeline ransomware event---invariably involve
\emph{chains}: initial access through one weakness, lateral movement
through another, privilege escalation through a third, and
consequential action through a fourth. Any automated red team that
stops at atomic findings will systematically miss the class of attacks
operators most need to know about.

Our ChainReactor work [Pasquale et al., USENIX Security 2024] demonstrated that AI
planning---specifically, PDDL-based planning over atomic attacks
characterized by preconditions and postconditions---can discover
privilege-escalation chains in Unix environments that even expert
red-teamers missed. \sysname extends this approach in three directions.

\paragraph{Domain expansion.}
Where ChainReactor operated on a single host, \sysname operates on a
multi-host, multi-protocol, \cps-wide domain. We will extend the
PDDL formulation to model network segments, protocol-specific
attacker capabilities, and physical-process effects (e.g., ``setpoint
modified''). The state-space explosion that results will be managed
by a combination of hierarchical planning (plan at the subnet level,
then refine within) and LLM-guided heuristic search, in which a
language model proposes candidate next steps that a classical planner
then validates.

\paragraph{Grounded plan synthesis with LLMs.}
Recent evaluations show that AI agents are making measurable progress
on multi-step attack scenarios, and that even relatively small models
can propose plausible attack steps when given appropriate context.
However, LLMs are also known to hallucinate preconditions and
postconditions, which is unacceptable for an automated red team. We
will investigate a hybrid approach in which LLMs propose candidate
attack plans in natural language, a grounding module converts each
step into PDDL actions (refusing steps that do not correspond to
atomic findings in the KB), and a classical planner validates the
result. Our recent experience with the Artiphishell system in the
DARPA AIxCC competition provides a working foundation for this style
of LLM/classical-planner hybrid.

\paragraph{Attack execution and confirmation.}
A plan that is valid on paper is not yet evidence of a vulnerability.
\sysname instantiates the twin, executes the plan against it using a
library of attack primitives implemented as Python agents, and checks
whether the nominated flag is reached. Successful plans are replayed
on a clean twin snapshot to eliminate side-effects introduced by
earlier attempts. Failed plans are examined for their failure reasons,
which are written back into the KB and used to refine future planning.

\subsubsection{Findings Triage and Human Escalation}

An unfiltered agentic red team will generate more findings than a
human team can validate. \sysname therefore includes a triage stage
that ranks findings before presenting them. The ranking draws on four
signals: the \emph{confidence} with which the KB entities supporting
the finding are grounded in observations (as opposed to documentation
alone); the \emph{consequence class} of the compromised flag (as
defined in the operator's security policy); the \emph{path length} of
the attack (shorter chains are more likely to be realistic); and the
\emph{novelty} of the finding relative to previously-reported ones.
Triage is itself an agentic process, and its outputs are auditable:
the analyst receives a ranked list with a short natural-language
justification for each item, and can drill into the provenance trace
that supports it.

\subsubsection{False Positives and the Fidelity Feedback Loop}

When a finding is labeled as a false positive by the human analyst,
the cause is almost always one of two things: a divergence between
the twin and the real system (``that port isn't actually open in
production''), or a policy misalignment (``that user does have
legitimate access to that resource''). Both cases produce structured
feedback into the KB. Divergences trigger the Observer Agents to
re-investigate the relevant corner of the system; policy
misalignments trigger a KB update that Red Team Agents will consider
in future planning. This closed loop is what distinguishes \sysname
from a one-shot penetration test: over time, both the twin's fidelity
and the red team's precision should improve.

\subsubsection{Expected Outcomes of Thrust~3}
\begin{itemize}[leftmargin=1.3em,itemsep=0.1em,topsep=0.2em]
  \item A PDDL-based attack-planning domain for multi-host, multi-protocol
  \cps environments, together with a hybrid LLM/classical planner.
  \item An open-source agentic red-team framework that composes
  component-level analyses into end-to-end attack plans, executable
  against \sysname digital twins.
  \item An empirical study on reference \CPSs of the precision, recall,
  and path-length distribution of discovered attacks, with comparison
  to human-red-team baselines where available.
\end{itemize}
