\section{Timeline}
\label{sec:timeline}

The project is planned as a three-year effort, with thrusts serialized
in their primary focus but running in parallel at a lower intensity so
that an end-to-end prototype exists from the first year.

\paragraph{Year 1: Knowledge Base and Observation.}
Primary focus on Thrust~1. We will design and implement the hybrid
KB, develop the first generation of passive observation modules
(network, log, configuration), and deploy them on the UCSB internal
network and on the water-treatment reference testbed. By the end of
Year~1, a rudimentary Replication Agent and Red Team Agent will
operate against a hand-built twin of the water-treatment testbed,
establishing the end-to-end loop.

\paragraph{Year 2: Replication.}
Primary focus on Thrust~2. We will formalize and implement the
controlled-fidelity replication algorithm, integrate QEMU, HALucinator,
and Conware-derived mock synthesis, and extend the Replication Agent
to consume the KB automatically. A second reference testbed
(building automation) and at least one partner environment will be
brought into the evaluation. Year~2 deliverables include a quantitative
study of twin fidelity on the water-treatment testbed.

\paragraph{Year 3: Analysis and integration.}
Primary focus on Thrust~3. We will develop the PDDL-based planning
domain for multi-host \cps environments, implement the LLM/classical
hybrid planner, integrate component-level analyses as sources of
atomic findings, and run end-to-end red-team campaigns on all three
reference testbeds. Year~3 will also include a longitudinal evaluation
of the feedback loop: how much does twin fidelity and red-team
precision improve over successive iterations of analyst validation?

\paragraph{Cross-cutting activities.}
Open-source releases, publications, student involvement, and the
annual CPS-focused CTF competition (\S\ref{sec:broader}) run across
all three years. Each thrust produces artifacts that feed the others,
and the end-to-end prototype is maintained continuously rather than
assembled at the end.
