\section{Results from Prior NSF Support}
\label{sec:prior}

\paragraph{SaTC: CORE: Medium: Bedrock: Security for Smart Contracts.}
\emph{Award number:} CNS-2334709.
\emph{Amount:} \$1{,}200{,}000.
\emph{Dates:} 6/1/2024--5/31/2027.

\emph{Intellectual merit.}
This project is developing the first multi-chain program analysis
platform that operates directly on low-level smart contract bytecode.
The platform enables analyses to be reused across different blockchain
environments and supports unified modeling of multi-chain applications
such as bridges. The techniques developed under this award are also
identifying higher-level logic flaws in smart contracts that are
invisible to single-chain, source-level tools.

\emph{Broader impacts.}
Attacks against smart contracts pose a significant threat to the Web3
ecosystem and its users: millions of dollars are lost each week to
attacks against DeFi applications, affecting both organizations and
individuals. The protection techniques developed under this award
offer opportunities for societal and industrial impact, and the
project is producing open-source artifacts that are being used by
security practitioners working in the blockchain space.

\emph{Publications and products.}
Results from this award are being published in top-tier security
venues, and software artifacts produced under the award are being
released under open-source licenses on the PIs' group repositories.
Updated lists of publications and artifacts are maintained at the PIs'
group website.
